---
title: "Analysis and Result"
output: html_document
---

## Analysis

The one-sample t-test on the difference scores revealed a significant difference between self-perceived attractiveness and the average perception by others. The negative t-value (-7.0355) indicates that, on average, individuals tend to overestimate their own attractiveness compared to how others perceive them. The extremely low p-value (1.256e-11) supports the rejection of the null hypothesis, further emphasizing the substantial difference in self-perceived attractiveness.

The 95 percent confidence interval for the true mean difference is (-0.9838924, -0.5538447). This interval does not include zero, reinforcing the conclusion that individuals exhibit a systematic bias by viewing themselves as more attractive than how others perceive them.

In summary, the numerical results strongly support the conclusion that individuals have a tendency to be overly confident in their self-perceived attractiveness. The statistical evidence indicates a consistent pattern of overestimation, shedding light on the dynamics of self-perception in social contexts.

```{r message=FALSE, warning=FALSE, include=FALSE}
library(here)
library(tidyverse)
data <- read.csv(paste0(here(),'/data/Speed_Dating_Data.csv'))
```

```{r message=FALSE, warning=FALSE,echo=FALSE}
data %>% select(iid,pid,attr,attr3_1,attr5_1,attr5_2,attr5_3) %>%
  filter(!is.na(attr5_1)) %>%
  group_by(iid,attr5_1) %>%
  summarise(attr_other_rating=mean(attr,na.rm = TRUE)) %>%
  pivot_longer(cols = c(attr5_1,attr_other_rating),values_to = 'Score', names_to = 'Rating Type') %>%
  ggplot(aes(x=`Rating Type`,y=Score)) +
  geom_violin() +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2) +
  scale_x_discrete(label=c('Other Rating','Self Rating')) +
  ggtitle('Distributions of Other Rating and Self Rating') 
```

```{r message=FALSE, warning=FALSE,echo=FALSE}
data %>% select(iid,pid,attr,attr3_1,attr5_1,attr5_2,attr5_3) %>%
  filter(!is.na(attr5_1)) %>%
  group_by(iid,attr5_1) %>%
  summarise(attr_other_rating=mean(attr,na.rm = TRUE)) %>%
  ggplot(aes(x=attr_other_rating,y=attr5_1)) +
  geom_density_2d() +
  xlab('Self Rating') +
  ylab('Other Rating') +
  ggtitle('Contour Plot of Self Rating and Other Rating')
```

```{r message=FALSE, warning=FALSE,echo=FALSE}
data %>% select(iid,pid,attr,attr3_1,attr5_1,attr5_2,attr5_3) %>%
  filter(!is.na(attr5_1)) %>%
  group_by(iid,attr5_1) %>%
  summarise(attr_other_rating=mean(attr,na.rm = TRUE)) %>%
  t.test(x=.$attr_other_rating,y=.$attr5_1,alternative='two.sided',paired = TRUE,mu=0)
```

```{r message=FALSE, warning=FALSE,echo=FALSE}
data %>% select(iid,pid,attr,attr3_1,attr5_1,attr5_2,attr5_3) %>%
  filter(!is.na(attr5_1)) %>%
  group_by(iid,attr5_1) %>%
  summarise(attr_other_rating=mean(attr,na.rm = TRUE)) %>%
  mutate(diff=attr_other_rating-attr5_1) %>%
  t.test(x=.$diff,y=NULL,alternative='two.sided',mu=0,paired=FALSE)
```

```{r message=FALSE, warning=FALSE,echo=FALSE}
data %>% select(iid,pid,attr,attr3_1,attr5_1,attr5_2,attr5_3) %>%
  filter(!is.na(attr5_1)) %>%
  group_by(iid,attr5_1) %>%
  summarise(attr_other_rating=mean(attr,na.rm = TRUE)) %>%
  mutate(diff=attr_other_rating-attr5_1) %>%
  cor.test(x=.$attr_other_rating,y=.$attr5_1,alternative='greater',method='pearson')
```
